hbm_paper_results

### 2024-01-19 paper_lbcc_results.Rmd

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")
source("./cubic_scripts/R_scripts/ranked_welch_tests.R")
aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")
```

>>>>

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")
source("./cubic_scripts/R_scripts/ranked_welch_tests.R")
aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")

data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/lifespan"
```

# QC ComBat Outputs

csvs scp'd from cubic

Log-Scaled

```{r}
imp.sites_log.cf_cf.gam <- fread(file=paste0(data_path, "/lifespan-CN-imp-sites_log-cf_cf.gam_data.csv"))
sum(is.na(imp.sites_log.cf_cf.gam))
sum(imp.sites_log.cf_cf.gam < 0)
skimr::skim(imp.sites_log.cf_cf.gam$lh_Vol_posteriorcingulate)
min(imp.sites_log.cf_cf.gam$lh_Vol_posteriorcingulate)
```

```{r}
imp.sites_log.cf_cf.gamlss <- fread(file=paste0(data_path, "/lifespan-CN-imp-sites_log-cf_cf.gamlss_data.csv"))
sum(is.na(imp.sites_log.cf_cf.gamlss))
skimr::skim(imp.sites_log.cf_cf.gam$log_age)
skimr::skim(imp.sites_log.cf_cf.gam$sex)
skimr::skim(imp.sites_log.cf_cf.gam$sex.age)
skimr::skim(imp.sites_log.cf_cf.gam$fs_version)
skimr::skim(imp.sites_log.cf_cf.gam$Vol_total)
```

Min Val Shift

```{r}

```
